---
title: "Regression Model"
author: "Nick Orka"
date: "1/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary

This work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

## Exploratory Analysis

```{r, echo=TRUE}
str(mtcars)
df <- within(mtcars, {
   vs <- factor(vs, labels = c("V", "S"))
   am <- factor(am, labels = c("automatic", "manual"))
   cyl  <- factor(cyl)
   gear <- factor(gear)
   carb <- factor(carb)
})
summary(df)

```

## Regression Models
```{r,echo=TRUE}
ttest <- t.test(df[df$am == 'automatic', 'mpg'],df[df$am == 'manual', 'mpg'])
ttest
```
The mpg difference between automatic and manual trasmission is significant (~7.25) according to p-value (. we have to reject null hiphotesis.

Let's check how mpg correlates with all other variables:
```{r, fig.width=12, fig.height=12, echo=FALSE}
pairs(mpg ~ ., data = df)
```
As we can see all other variables correlate with mpg but only a part of them correlate with transmission type: disp, hp, wt, qsec.

Let's create direct model between MPG and AM variables.
```{r,echo=TRUE}
m1 <- lm(mpg ~ am, data = df)
summary(m1)
```


The intercept tells us that the median of Automatic is 17.14 and the median of Manual is 7.24 units higher. The p-value for this model is 0.000285, which tells us that the coefficients are statistically significant. Finally, Transmission explains 36% of the variance between means, it might be suitable to explore more variables so the variance can be explained better. Now we compute following models.
```{r}
m2 <- lm(mpg ~ am + disp, data = df)
m3 <- lm(mpg ~ am + disp + hp, data = df)
m4 <- lm(mpg ~ am + disp + hp + wt, data = df)
m5 <- lm(mpg ~ am + disp + hp + wt + qsec, data = df)
m <- c(am=m1$coef[2], disp=m2$coef[2], hp=m3$coef[2], wt=m4$coef[2], qsec=m5$coef[2])
m
summary(m)
```
It shows us that manual transmission coefficient allways positive, no matter what variable we do include in the models.
```{r}
anova(m1, m2, m3, m4, m5)
```
In this comparison we can see that there are other variables that are statistically significant. Let's take a look at the model with all of them:
```{r}
summary(m5)
```

Now the variance in MPG is exaplained better with the inclussion of other variables (R-squared=86%). The p-value also is less than 0.05. Finally, check for homoskedastic in the appendix and according to the behaviour of the residuals this assumption holds.

## Conclusion

Manual transmission inscreases MPG by means of 3.47, which is exact match for the median of different models. 

## Appendix
```{r,echo=TRUE}
boxplot(mpg~am,data = df,col=c('blue','red'),ylab='MPG',xlab='Transmission',main='MPG ~ Transmittion')
```


```{r,echo=TRUE}
par(mfrow = c(2,2))
plot(m5)
```